---
title: "Analysis of the *mtcars* Dataset"
author: "Joan Marine-Boada"
date: "30/04/2021"
output: ioslides_presentation
---

## The goal of our analysis

The relationship between miles per gallon (MPG) and the other variables of the dataset. 
We have a data set of a collection of cars, and we are interested in exploring the relationship between a set of variables and miles per gallon (MPG).
The App user can choose the variable which he wants to compare, and we display a plot of a boxplot and the linear regression analysis. The user can choose too if the outliers appear or not.

The *mtcars* Dataset was extracted from the 1974 Motor Trend US magazine,and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models)

## The Dataset Format

We work with a data frame with 32 observations on 11 (numeric) variables.

Let's look the first rows:

```{r, comment=""}
library(datasets)
head(mtcars)
```

## The *MPG* variable

Due to our analysis is centered on the relationship between miles per gallon (MPG) and the other variables, let's look at our main variable:

```{r, comment=""}
summary(mtcars$mpg)
```

## The *MPG* variable

We can see the distribution's shape of the variable if we plot its histogram.

```{r, echo=FALSE}
library(ggplot2)
g<-ggplot(mtcars, aes(x=mpg))+
    theme_bw()+ 
    geom_histogram(alpha=0.3,
                   binwidth=5.5,
                   colour="gold2", 
                   fill="gold2")+
    theme(axis.title.x=element_text(size=20),
          axis.title.y=element_text(size=20))+
    xlab("MPG")+
    ylab("Frequency")
g
```
